\documentclass[11ot]{article}

\input{structure}
\makeindex

\title{Gruppe 15\\Bruk av maskinsyn for deteksjon av ulike fiskearter}
\author{Hans Alan Whitburn Haugen\\Veileder: Eirin Bar}

\begin{document}
\pagenumbering{gobble}
\input{titlepage}
\newpage
\include{abstract}
\newpage
\input{sections/abbreviations}
\newpage
\include{thanks}
\newpage

\tableofcontents
\clearpage
\pagenumbering{arabic}
\setcounter{page}{1}

\include{sections/introduction}
\include{sections/theory}
\include{sections/method}
\include{sections/analysis}
\include{sections/discussion}
\include{sections/end}

\begin{thebibliography}{9}
\addcontentsline{toc}{section}{Referanser}
% 137 ABCDEFGHIJKLMNOPQRSTUVXYZ

\bibitem{Angell og Ekanger 2017} 
Angell E., og Ekanger A. 
\textit{Fekk fisk med magen full av oppdrettsfôr}. 
NRK, \url{https://www.nrk.no/vestland/fekk-fisk-med-magen-full-av-oppdrettsfor-1.13677856}, 2017. (hentet 24. April 2020)

\bibitem{Batanina 2020} 
Batanina L.
\textit{Feature-request: State-of-art Yolo v4 Detector}. 
Github \url{https://github.com/opencv/opencv/issues/17148}, 2020. (hentet 6. Mai 2020)

\bibitem{Bochkovskiy 2020} 
Bochkovskiy A.
\textit{YOLOv4 (v3/v2)}. 
Github \url{https://github.com/AlexeyAB/darknet}, 2020. (hentet 6. Mai 2020)

\bibitem{Bochkovskiy m.fl. 2020} 
Bochkovskiy A, Wang C.Y., og Liao H.Y. M.
\textit{YOLOv4: Optimal Speed and Accuracy of Object Detection}. 
arXiv.org \url{https://arxiv.org/abs/2004.10934}, 2020. (hentet 8. Mai 2020)

\bibitem{IanBuck} 
Buck I.
\textit{Stream Computing on Graphics Hardware}. 
Stanford University \url{http://graphics.stanford.edu/~ianbuck/thesis.pdf}, 2006. (hentet 6. Mai 2020)

\bibitem{Baevre-Jensen 2019} 
Bævre-Jensen M.
\textit{Kostnadene for norsk lakseoppdrett fortsetter å øke også i 2019}. 
Fiskeri- og havbruksnæringens forskningsfinansiering (FHF) \url{https://www.fhf.no/nyheter/nyhetsarkiv/kostnadene-for-norsk-lakseoppdrett-fortsetter-aa-oeke-ogsaa-i-2019}, 2019. (hentet 6. Mai 2020)

\bibitem{primate} 
Cadieu C. F., Hong H., Yamins D. L. K., Pinto N., Ardila D., Solomon E. A., Majaj N. J., og DiCarlo J. J. 
\textit{Deep Neural Networks Rival the Representation of Primate IT Cortex for Core Visual Object Recognition}. 
PLOS Computational Biology, 2014.

\bibitem{Christensen 2019} 
Christensen T. B. 
\textit{Fôrer villfisk med lusegift og medisiner}. 
Naturvernforbundet, \url{https://naturvernforbundet.no/naturogmiljo/forer-villfisk-med-lusegift-og-medisiner-article39320-1024.html}, 2019. (hentet 24. April 2020)

\bibitem{Canziani m.fl 2017} 
Canziani A., Culurciello E., og Paszke A. 
\textit{An Analysis of Deep Neural Network Models for Practical Applications}. 
Weldon School of Biomedical Engineering Purdue University, Faculty of Mathematics, Informatics and Mechanics University of Warsaw, 2017.

\bibitem{deepfish} 
Cui S., Zhou Y., Wang Y., og Zhai L. 
\textit{Fish Detection Using Deep Learning}. 
Applied Computational Intelligence and Soft Computing, 2020.

\bibitem{distributed} 
Dean J., Corrado G. S., Monga R., Chen K., Devin M., Le Q. V., Mao M. Z., Ranzato M., Senior A., Tucker P., Yang K., og Ng A. Y. 
\textit{Large Scale Distributed Deep Networks}. 
Google Inc., Mountain View, CA, 2012.

\bibitem{math} 
Dumoulin V., og Visin F. 
\textit{A guide to convolution arithmetic for deep learning}. 
MILA, Université de Montréal, AIRLab, Politecnico di Milano, 2018.

\bibitem{Falstad 2016} 
Falstad S. V.
\textit{Suksess med vaksinemaskin}. 
Trønder-avisa \url{https://www.t-a.no/nyheter/2016/02/01/Suksess-med-vaksinemaskin-12104745.ece}, 2016. (hentet 6. Mai 2020)

\bibitem{Fenstad 2019} 
Fenstad A.
\textit{Nå kan maskinen skille mellom makrell og sild}. 
tu.no \url{https://www.tu.no/artikler/na-kan-maskinen-skille-mellom-makrell-og-sild/464208?utm_source=newsletter-tudaily&utm_medium=email&utm_campaign=newsletter-2019-05-06}, 2019. (hentet 6. Mai 2020)

\bibitem{Girshick 2015} 
Girshick R. 
\textit{Fast R-CNN}. 
Microsoft Research, 2015.

\bibitem{semantic_segmentation} 
Girshick R., Donahue J., Darrell T., og Malik J. 
\textit{Rich feature hierarchies for accurate object detection and semantic segmentation}. 
UC Berkeley, 2014.

\bibitem{Goodfellow m.fl. 2016} 
Goodfellow I., Bengio Y., og Courville A. 
\textit{Deep Learning}. 
MIT Press \url{www.deeplearningbook.org}, 2016. (hentet 26. April 2020)

\bibitem{resnet} 
He K., Zhang X., Ren S., og Sun J. 
\textit{Deep Residual Learning for Image Recognition}. 
Microsoft Research, 2015.

\bibitem{stochastic_depth} 
Huang G., Sun Y., Liu Z., Sedra D., og Weinberger K. Q. 
\textit{Deep Networks with Stochastic Depth}. 
Cornell University, Tsinghua University, 2016.

\bibitem{hubel} 
Hubel D. H., og Wiesel T. N. 
\textit{Receptive Fields of Single Neurones in the Cat's Striate Cortex}. 
 Wilmer Institute, The Johns Hopkins Hospital and University, Baltimore, Maryland, U.S.A., 1959.
 
\bibitem{Hustad og Svalheim 2020} 
Hustad A., og Svalheim R.
\textit{Hvem bryr seg om pelletssei?}. 
Nofima \url{https://www.fhf.no/nyheter/nyhetsarkiv/kostnadene-for-norsk-lakseoppdrett-fortsetter-aa-oeke-ogsaa-i-2019}, 2019. (hentet 6. Mai 2020)

\bibitem{batchnorm} 
Ioffe S., og Szegedy C. 
\textit{Batch Normalization: Accelerating Deep Network Training by Reducing Internal Covariate Shift}. 
Google Inc, 2015.

\bibitem{Jakobsen 2017} 
Jakobsen A. N.
\textit{Fikk torsk full av oppdrettsfôr: – Motbydelig fisk}. 
NRK, \url{https://www.nrk.no/tromsogfinnmark/fikk-torsk-full-av-oppdrettsfor_-_-motbydelig-fisk-1.13662637}, 2017. (hentet 24. April 2020)

\bibitem{seaclef} 
Jäger J., Rodner E., Denzler J., Wolff V., og Fricke-Neuderth K. 
\textit{SeaCLEF 2016: Object proposal classification for fish detection in underwater videos}. 
Department of Electrical Engineering and Information Technology, Fulda University of Applied Sciences, Germany, Computer Vision Group, Friedrich Schiller University Jena, Germany, 2016.

\bibitem{captioning} 
Johnson J., Karpathy A., og Fei-Fei L. 
\textit{DenseCap: Fully Convolutional Localization Networks for Dense Captioning}. 
Department of Computer Science, Stanford University, 2015.

\bibitem{kaller} 
Kaller J. 
\textit{Methods of Data Labeling in Machine Learning}. 
Blog \url{https://medium.com/ai%C2%B3-theory-practice-business/methods-of-data-labeling-in-machine-learning-80a34ece6c8b}, 2019. (hentet 18. mai 2020)

\bibitem{andrej} 
Karpathy A. 
\textit{Convolutional Neural Networks}. 
Stanford University \url{https://www.youtube.com/watch?v=bNb2fEVKeEo}, 2014. (hentet 13. mai 2020)

\bibitem{ImageNet} 
Krizhevsky A., Sutskever  I., og Hinton G. E.. 
\textit{ImageNet Classification with Deep Convolutional Neural Networks}. 
University of Toronto, 2012.

\bibitem{docreg} 
LeCun Y., Bottou L., Bengio Y., og Haner P. 
\textit{Gradient-Based Learning Applied to Document Recognition}. 
IEEE, 1998.

\bibitem{flow} 
Lin C.E. 
\textit{Introduction to Motion Estimation with Optical Flow}. 
nanonets \url{https://nanonets.com/blog/optical-flow/}, 2019. (hentet 16. mai 2020)

\bibitem{coco} 
Lin T.Y., Maire M., Belongie S., Bourdev L., Girshick R., Hays J., Perona P., Ramanan D., Zitnick C. L., og Dollár P. 
\textit{Microsoft COCO: Common Objects in Context}. 
Microsoft, 2015.

\bibitem{retinanet} 
Lin T.Y., Goyal P., Girshick R., He K., Dollár P.
\textit{Focal Loss for Dense Object Detection}
Facebook AI Research, 2018.

\bibitem{kato} 
Lindberg S.K. 
\textit{Video av torsk og sei fra Havbruksstasjonen i Tromsø}. 
Nofima, 2020.

\bibitem{Mallick m.fl. 2020} 
Mallick S., Gupta V., Murzova A., Petrovicheva A., Serebryakov G., Semkin P., Chandra P., Belousov S., Khanova T., og Koriukina V.
\textit{Deep Learning with PyTorch}. 
OpenCV.org \url{https://courses.opencv.org}, 2020. (hentet 14. Mai 2020)

\bibitem{Nielsen 2019} 
Nielsen M. 
\textit{Using neural nets to recognize handwritten digits}. 
\url{http://neuralnetworksanddeeplearning.com/chap1.html}, 2019. (hentet 28. April 2020)

\bibitem{nrk 2018} 
NRK. 
\textit{Laks med medisinrester har rømt fra Marine Harvest-anlegg}. 
NRK, \url{https://www.nrk.no/trondelag/laks-har-romt-fra-marine-harvest-anlegg-i-naeroy-1.13902322}, 2019. (hentet 25. April 2020)

\bibitem{Oshri 2019} 
Oshri G. 
\textit{Introducing TensorBoard.dev: a new way to share your ML experiment results}. 
Google Inc., \url{https://blog.tensorflow.org/2019/12/introducing-tensorboarddev-new-way-to.html}, 2019. (hentet 17. Mai 2020)

\bibitem{Olsen 2019} 
Olsen J. E. 
\textit{Ny oppmerksomhet rundt “pellets-fisken”}. 
fiskeribladet, \url{https://fiskeribladet.no/nyheter/?artikkel=69867}, 2019. (hentet 24. April 2020)

\bibitem{Olsen m.fl. 2018} 
Olsen O.C., Johansen J. I., og Grov B. 
\textit{Villfisk mettes av oppdrettsmat: – Jeg blir rett og slett forbanna}. 
NRK, \url{https://www.nrk.no/nordland/villfisk-mettes-av-oppdrettsmat_-_-jeg-blir-rett-og-slett-forbanna-1.14003547}, 2018. (hentet 24. April 2020)

\bibitem{OpenCV Team 2020} 
OpenCV Team. 
\textit{About OpenCV}. 
OpenCV \url{https://opencv.org/about/}, 2020. (hentet 5. Mai 2020)

\bibitem{Redmon 2016} 
Redmon J. 
\textit{Darknet: Open Source Neural Networks in C}. 
\url{http://pjreddie.com/darknet/}, 2013-2016.

\bibitem{Redmon 2018} 
Redmon J. 
\textit{YOLOv3: An Incremental Improvement}. 
arXiv, 2018.

\bibitem{Ren m.fl. 2016} 
Ren S., He K., Girshick R., og Sun J.
\textit{Faster R-CNN: Towards Real-Time Object Detection with Region Proposal Networks}. 
University of Science and Technology of China, Microsoft Research, 2016.

\bibitem{Robertsen 2020} 
Robertsen R. 
\textit{Sameksistens av marine næringer i kystsonen}. 
Nofima, \url{https://nofima.no/prosjekt/sameksistens}, 2020.

\bibitem{marinescience} 
Salman A, Siddiqui S. A. , Shafait F., Mian A., Shortis M. R., Khurshid K., Ulges A., og Schwanecke U. 
\textit{Automatic fish detection in underwater videos by a deep neural network-based hybrid motion learning system}. 
ICES Journal of Marine Science, 2019.

\bibitem{Debt} 
Sculley D., Holt G., Golovin D., Davydov E., Phillips T., Ebner D., Chaudhary V., Young M., Crespo J.F., og Dennison D. 
\textit{Hidden Technical Debt in Machine Learning Systems}. 
Google Inc., 2015.

\bibitem{entropy} 
Shannon C. E. 
\textit{A Mathematical Theory of Communication}. 
Bell Labs, 1948.

\bibitem{texton_forests} 
Shotton J., Johnson M., og Cipolla R. 
\textit{Semantic Texton Forests for Image Categorization and Segmentation}. 
Toshiba Corporate R\&D Center Kawasaki, Japan, Department of Engineering University of Cambridge, UK, 2008.

\bibitem{autofish} 
Siddiqui S. A., Shafait F., Mian A. S., og Shortis M. R. 
\textit{Automatic fish species classification in underwater videos: Exploiting pretrained deep neural network models to compensate for limited labelled data}. 
ICES Journal of Marine Science, 2017.

\bibitem{vgg} 
Simonyan K., og Zisserman A. 
\textit{Very Deep Convolutional Networks for Large-Scale Image Recognition}. 
Visual Geometry Group, Department of Engineering Science, University of Oxford, 2015.

\bibitem{Spruill 2011} 
Spruill V.
\textit{Environmental Impacts of Open-Ocean Aquaculture}. 
Ocean Conservancy \url{https://issuu.com/oceanconservancy/docs/oc_rfts_v11_single}, 2011. (hentet 6. Mai 2020)

\bibitem{Szegedy m.fl. 2014} 
Szegedy C., Liu W., Jia Y., Sermanet P., Reed S., Anguelov D., Erhan D., Vanhoucke V., og Rabinovich A. 
\textit{Going deeper with convolutions}. 
Google Inc., University of Michigan, University of North Carolina, Chapel Hill, arXiv, 2014.

\bibitem{Saether 2017} 
Sæther B.S. 
\textit{Effekter av oppdrett på vill marin fisk}. 
Nofima, \url{https://nofima.no/nyhet/2017/09/effekter-av-oppdrett-pa-vill-marin-fisk/}, 2017. (hentet 24. April 2020)

\bibitem{The Apache Software Foundation 2004} 
The Apache Software Foundation 
\textit{Apache License, Version 2.0}. 
The Apache Software Foundation \url{https://www.apache.org/licenses/LICENSE-2.0}, 2004. (hentet 5. Mai 2020)

\bibitem{Trana m.fl. 2019} 
Trana K., Klausen D. H., og Bolstad J. 
\textit{Denne torsken er full av fôr fra oppdrettsnæringa}. 
NRK, \url{https://www.nrk.no/trondelag/fiskere-har-solgt-torsk-som-er-full-av-lakselusmiddel-_-vet-ikke-om-det-er-farlig-1.14742706}, 2019. (hentet 24. April 2020)

\bibitem{KentaroWada2020} 
Wada K.
\textit{labelme: Image Polygonal Annotation with Python}. 
Github \url{https://github.com/wkentaro/labelme}, 2016. (hentet 6. Mai 2020)

\bibitem{Wu2020} 
Wu Y., Kirillov A., Massa F., Lo W.Y., og Girshick R.
\textit{Detectron2}. 
Github \url{https://github.com/facebookresearch/detectron2}, 2020. (hentet 6. Mai 2020)

\bibitem{underwater} 
Xu W., og Matzner S. 
\textit{Underwater Fish Detection using Deep Learning for Water Power Applications}. 
Pacific Northwest National Laboratory, 2018.

\bibitem{yang} 
Yang M. Y., og Förstner W. 
\textit{A Hierarchical Conditional Random Field Model for Labeling and Classifying Images of Man-made Scenes}. 
Department of Photogrammetry, Institute of Geodesy and Geoinformation, University of Bonn Nussallee 15, 53115 Bonn, Germany, 2011.

%https://gilberttanner.com/blog/detectron2-train-a-instance-segmentation-model

\end{thebibliography}

\include{sections/appendix_code}
%\include{sections/appendix_azure}
%\include{sections/appendix_ssh}

\end{document}
