\section*{Forkortelser og faguttrykk}

\begin{description}

\item[Maskinsyn] Computer Vision has become ubiquitous in our society, with applications in search, image understanding, apps, mapping, medicine, drones, and self-driving cars. Core to many of these applications are visual recognition tasks such as image classification, localization and detection. Recent developments in neural network (aka “deep learning”) approaches have greatly advanced the performance of these state-of-the-art visual recognition systems. This course is a deep dive into details of the deep learning architectures with a focus on learning end-to-end models for these tasks, particularly image classification. During the 10-week course, students will learn to implement, train and debug their own neural networks and gain a detailed understanding of cutting-edge research in computer vision. The final assignment will involve training a multi-million parameter convolutional neural network and applying it on the largest image classification dataset (ImageNet). We will focus on teaching how to set up the problem of image recognition, the learning algorithms (e.g. backpropagation), practical engineering tricks for training and fine-tuning the networks and guide the students through hands-on assignments and a final course project. Much of the background and materials of this course will be drawn from the ImageNet Challenge.
\item[Backpropagation]
\item[Kunstige nevrale nettverk]
\item[Overfitting] overtilpasning er når nettverket kan detektere objekter på bilder fra treingsdatasettet, men kan ikke detektere objekter på noen andre bilder
\item[ImageNet]
\item[unix]
\item[Programvareutgivelse]
\item[COCO]
\item[bakgrunnssubtraksjon]
\item[Optical flow]
\item[API]
\item[KI] Kunstig Intelligens
\item[SVM] Support Vector Machine
\item[Kernel] også kjent som filter, kunstig nevron eller perceptron er en funksjon som består av vekter og bias, den tar inn matriser, abstrakte konsepter eller ``features'', og gir fra seg nye abstrakte konsepter, nye ``features'', basert på innmatningen.
\item[Maskinlæringsbiblioteker]
\item[TL] Transfer learning
\item[RetinaNet]
\item[Programvarebibliotek]
\item[Programvarerammeverk]
\item[Detectron2]
\item[ssh] Secure SHell
\item[Nettsky]
\item[Azure]
\item[darknet: Open-Source Neural Networks in C]
\item[PyTorch]
\item[Programvareutgivelse]
\item[Deep Learning]
\item[dnn] Deep Neural Networks
\item[ML] Machine Learning
\item[CPU] Central Processing Unit
\item[GPU] Graphical Processing Unit
\item[YOLO] You Only Look Once, real time object detection
\item[FPS] Frames Per Second
\item[State-of-the-art] 
\item[Real-time] Sanntid
\item[mAP] 
\item[Total loss]
\item[IoU] 
\item[Nøyaktighet] 
\item[Presisjon] 
\item[Modell] 
\item[Algoritme]


\end{description}